Hydra Battles and Cie

### 2021-09-08 doc/chapter-powers.tex
adapt chapter-powers to Alectryon (partial)

\begin{Coqsrc}
Section Nmodulo.
  Variable m : N.
  Hypothesis m_gt_1 : 1 < m.

  Definition mult_mod ( x y : N) := (x * y) mod m.
  Definition mod_eq ( x y: N) := x mod m = y mod m.

  Global Instance mod_equiv : Equiv N := mod_eq.

  Global Instance mod_op : Mult_op N := mult_mod.

  Global Instance mod_Equiv : Equivalence mod_equiv.
  (* Proof omitted *)

  Global Instance mult_mod_proper : 
  Proper (mod_equiv ==> mod_equiv ==> mod_equiv)  mod_op.
  (* Proof omitted *)

  Local Open Scope M_Scope.

  Lemma mult_mod_associative :  
  forall x y z,  x * (y * z) = x * y * z.
  (* Proof omitted *)

  Lemma one_mod_neutral_l  : forall x, 1 * x ==  x.
  (* Proof omitted *)

  Lemma one_mod_neutral_r  : forall x, x * 1 == x.
  (* Proof omitted *)

  Global Instance Nmod_Monoid : EMonoid  mod_op 1 mod_equiv.
  (* Proof omitted *)

End Nmodulo.

\paragraph{Example}
In the following interaction, we show how to instantiate the parameter \texttt{$m$} to a 
concrete value, for instance \texttt{$256$}.

\begin{Coqsrc}
Section S256.
Let mod256 :=  mod_op 256.
Local Existing Instance mod256 | 1.

Compute (211 * 67)
\end{Coqsrc}

\begin{Coqanswer}
= 57 : N  
\end{Coqanswer}

\begin{Coqsrc}
End S256.
\end{Coqsrc}

@@

\begin{Coqsrc}
Compute (211 * 67)%M.
\end{Coqsrc}

\begin{Coqanswer}
= 14137 : N   
\end{Coqanswer}

>>>>

\inputsnippets{Monoid_instances/Nmoduloa,
  Monoid_instances/Nmodulob, Monoid_instances/Nmoduloc,
  Monoid_instances/Nmodulod,
  Monoid_instances/Nmoduloe,
  Monoid_instances/Nmodulof,
  Monoid_instances/Nmodulog}

@@

\inputsnippets{Monoid_instances/Nmoduloh}

### 2021-09-08 doc/hydras.tex
adapt chapter-powers to Alectryon (partial)

\author{Pierre Castéran\\ LaBRI, Univ. Bordeaux, CNRS UMR 5800, \thanks{With contributions by Yves Bertot, \'Evelyne Contejean,  Jérémy Damour, Florian Hatat, Pascal Manoury, Clément Pit-Claudel, and Théo Zimmermann. The formalization of primitive recursive functions was originally authored by 
Russel O'Connor\cite{OConnor05}.}}
\date{\today}
%\date{August 2021}

>>>>

\author{Pierre Castéran\\ LaBRI, Univ. Bordeaux, CNRS UMR 5800, \thanks{With contributions by Yves Bertot, \'Evelyne Contejean,  Jérémy Damour, Florian Hatat, Pascal Manoury, Karl Palmskog, Clément Pit-Claudel, and Théo Zimmermann. The formalization of primitive recursive functions was originally authored by 
Russel O'Connor\cite{OConnor05}.}}
\date{\today}
%\date{August 2021}
